A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-07-17 博士/论文提交/adversarial_attack/TCSVT/response/response.tex

\textit{3. The technical novelty of this paper is not high as it directly borrows the approach from the traditional adversarial attack and use two additional path to train the neural networks. Can the authors provide theoretical analysis to explain the effectiveness based on such small change?}

% 其他跟踪攻击方法是复杂的，需要设定专门的损失函数和优化方法。我们的攻击方法是简单的，不需要设定专门的损失函数和优化方法。其他攻击方法是非通用的，我们的跟踪方法是通用的。我们之所以能够以简单的方案实现更困难的通用攻击，主要是因为我们放松了对扰动值的限制。如图所示，FAN的SSIM为0.92，我们的扰动的SSIM为0.56。
\textbf{
(1) On one hand, other attack methods on Siamese trackers are complex and require specialized loss functions and optimization methods, while our method is simple and dose not require specialized loss functions and optimization methods.
On the other hand, other attack methods on Siamese trackers are not universal while our method are doubly universal, both with respect to the data and the network architectures.
The main reason why it is possible to implement more difficult universal attacks in a simple scheme is that we relax the constraint on the value of the perturbations, achieving a balance between the attack ability and the perturbation perceptibility.
As shown in Figure \ref{fig:vis}, both FAN \cite{FAN} and our method can perform targeted attack. 
% 添加了由FAN生成的扰动的OTB的SSIM下降至0.92。添加了我们的扰动的OTB的SSIM下降至0.56。
The SSIM of OTB2015 perturbed by FAN drops to 0.92, while the SSIM perturbed by our method drops to 0.56.
By relaxing the constraint on the value of the perturbation, we can achieve better targeted attack performance on OTB2015.
Our method achieves a precision score of 0.795, compared to 0.420 for FAN.
}

\textbf{
(2) To the best of our knowledge, our work is the first attempt to generate video-agnostic perturbations to attack Siamese trackers. Besides FGSM \cite{FGSM} and Brown et al.'s work \cite{patch}, other adversarial example generation methods such as C\&W \cite{carlini2017towards} and PGD \cite{PGD} can also be integrated into our attacking system to further improve the attack effect.
In short, we focus on proposing a video-agnostic attacking system for Siamese trackers instead of proposing a specific adversarial example generation method.}

### 2021-07-17 博士/论文提交/adversarial_attack/TCSVT/latex/main.tex
改错。大版本完成。

% 题目
\hyphenation{op-tical net-works semi-conduc-tor}
\begin{document}
\title{A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking}
\author{
  Zhenbang Li, Yaya Shi, Jin Gao, Shaoru Wang, Bing Li, Pengpeng Liang, Weiming Hu
  \thanks{This work is supported by the national key R\&D program of china (No. 2018AAA0102802), the Natural Science Foundation of China (Grant No. 62036011, 61721004), the Key Research Program of Frontier Sciences, CAS, Grant No. QYZDJ-SSW-JSC040. \textit{(Corresponding author: Jin Gao.)}}

  \thanks{Z. Li, J. Gao, Shaoru Wang and B. Li are with the National Laboratory of Pattern Recognition, Institute of Automation, Chinese Academy of Sciences, Beijing, 100190, China, and also with School of Artificial Intelligence, University of Chinese Academy of Sciences, Beijing, 100190, China (e-mail: zhenbang.li@nlpr.ia.ac.cn; jin.gao@nlpr.ia.ac.cn; shaoru.wang@nlpr.ia.ac.cn; bli@nlpr.ia.ac.cn).}
  \thanks{Y. Shi is with the University of Science and Technology of China, Anhui, 230026, China (e-mail: shiyaya@mail.ustc.edu.cn).}
  \thanks{P. Liang is with Zhengzhou University, Henan, 450001, China (e-mail: liangpcs@gmail.com).}
  \thanks{W. Hu is with CAS Center for Excellence in Brain Science and Intelligence Technology, National Laboratory of Pattern Recognition, Institute of Automation, Chinese Academy of Sciences, Beijing, 100190, China, and also with School of Artificial Intelligence, University of Chinese Academy of Sciences, Beijing, 100190, China (e-mail: wmhu@nlpr.ia.ac.cn).}
}

@@

In this paper, we make the first attempt in finding the universal perturbations (Figure \ref{fig:UAP}) that fool a state-of-the-art Siamese tracker, \ie, SiamFC++ \cite{SiamFC++}, in a targeted attack manner, which comes at virtually no cost in the online-tracking phase. Specifically, we aim to attack the trackers by adding a universal perturbation to the template image and adding a \textit{fake target}, \ie, a small universal adversarial patch, into the search image adhering to the predefined trajectory (as shown in Figure \ref{fig:1}), so that the tracker outputs the location and size of the \textit{fake target} instead of the real target. Our generated video-agnostic perturbations allow perturbing a novel video to come at no additional cost except the mere addition operations -- and not require gradient optimization or network inference. Experiment results on OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k} and LaSOT \cite{GOT-10k} benchmarks demonstrate the effectiveness and efficiency of our approach.

@@

Recently, some Siamese trackers~\cite{SiamRPN,SiamRPN++,SiamFC++} have demonstrated a significant performance improvement in visual tracking. 
In particular, SiamRPN \cite{SiamRPN} consists of one Siamese subnetwork for feature extraction and another region proposal subnetwork including the classification and regression branches separately. Based on its success in the decomposition of classification and state estimation, SiamRPN++ \cite{SiamRPN++} further breaks the restriction of strict translation invariance through a simple yet effective spatial aware sampling strategy and successfully trains a ResNet-driven Siamese tracker with significant performance gains. Apart from these anchor-based methods, an anchor-free tracker SiamFC++ \cite{SiamFC++} is further designed by considering non-ambiguous scoring, prior target scale/ratio distribution, knowledge-free and estimation quality assessment guidelines.
In our experiments, we are focused on the anchor-free SiamFC++ tracker, whereas the transferability of our generated adversarial attacks to the previous anchor-based trackers is also studied.

@@

Adversarial attacks \cite{9169672} to image classification were first investigated in \cite{intriguing}, which is aimed to identify the vulnerability of modern deep networks to imperceptible perturbations. 
Recent studies also emerge to investigate the adversarial attacks to other diverse types of tasks such as natural language processing \cite{generating,zhang2020adversarial,morris2020textattack,jin2020bert} and object detection \cite{wei2019transferable}.
Scenarios of possible adversarial attacks can be categorized along different dimensions.

>>>>

% 题目
\hyphenation{op-tical net-works semi-conduc-tor}
\begin{document}
\title{A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking}
\author{
  Zhenbang Li, Yaya Shi, Jin Gao, Shaoru Wang, Bing Li, Pengpeng Liang, Weiming Hu
  \thanks{This work is supported by the National Key R\&D Program of China (No. 2018AAA0102802), the Natural Science Foundation of China (Grant No. 62036011, 61721004), the Key Research Program of Frontier Sciences, CAS, Grant No. QYZDJ-SSW-JSC040. \textit{(Corresponding author: Jin Gao.)}}

  \thanks{Z. Li, J. Gao, S. Wang and B. Li are with the National Laboratory of Pattern Recognition, Institute of Automation, Chinese Academy of Sciences, Beijing, 100190, China, and also with School of Artificial Intelligence, University of Chinese Academy of Sciences, Beijing, 100190, China (e-mail: zhenbang.li@nlpr.ia.ac.cn; jin.gao@nlpr.ia.ac.cn; shaoru.wang@nlpr.ia.ac.cn; bli@nlpr.ia.ac.cn).}
  \thanks{Y. Shi is with the University of Science and Technology of China, Anhui, 230026, China (e-mail: shiyaya@mail.ustc.edu.cn).}
  \thanks{P. Liang is with Zhengzhou University, Henan, 450001, China (e-mail: liangpcs@gmail.com).}
  \thanks{W. Hu is with CAS Center for Excellence in Brain Science and Intelligence Technology, National Laboratory of Pattern Recognition, Institute of Automation, Chinese Academy of Sciences, Beijing, 100190, China, and also with School of Artificial Intelligence, University of Chinese Academy of Sciences, Beijing, 100190, China (e-mail: wmhu@nlpr.ia.ac.cn).}
}

@@

In this paper, we make the first attempt in finding the universal perturbations (Figure \ref{fig:UAP}) that fool a state-of-the-art Siamese tracker, \ie, SiamFC++ \cite{SiamFC++}, in a targeted attack manner, which comes at virtually no cost in the online-tracking phase. Specifically, we aim to attack the trackers by adding a universal perturbation to the template image and adding a \textit{fake target}, \ie, a small universal adversarial patch, into the search image adhering to the predefined trajectory (as shown in Figure \ref{fig:1}), so that the tracker outputs the location and size of the \textit{fake target} instead of the real target. Our generated video-agnostic perturbations allow perturbing a novel video to come at no additional cost except the mere addition operations -- and not require gradient optimization or network inference. Experiment results on OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k}, LaSOT \cite{GOT-10k}, UAV123 \cite{UAV123}, VOT1016 \cite{VOT2016}, VOT2018 \cite{VOT2018} and VOT2019 \cite{VOT2019}. benchmarks demonstrate the effectiveness and efficiency of our approach.

@@

Recently, some Siamese trackers~\cite{SiamFC++,SiamRPN,SiamRPN++} have demonstrated a significant performance improvement in visual tracking. 
In particular, SiamRPN \cite{SiamRPN} consists of one Siamese subnetwork for feature extraction and another region proposal subnetwork including the classification and regression branches separately. Based on its success in the decomposition of classification and state estimation, SiamRPN++ \cite{SiamRPN++} further breaks the restriction of strict translation invariance through a simple yet effective spatial aware sampling strategy and successfully trains a ResNet-driven Siamese tracker with significant performance gains. Apart from these anchor-based methods, an anchor-free tracker SiamFC++ \cite{SiamFC++} is further designed by considering non-ambiguous scoring, prior target scale/ratio distribution, knowledge-free and estimation quality assessment guidelines.
In our experiments, we are focused on the anchor-free SiamFC++ tracker, whereas the transferability of our generated adversarial attacks to the previous anchor-based trackers is also studied.

@@

Adversarial attacks \cite{9169672} to image classification were first investigated in \cite{intriguing} with the aim of identifying the vulnerability of modern deep networks to imperceptible perturbations. 
Recent studies also emerge to investigate the adversarial attacks to other diverse types of tasks such as natural language processing \cite{generating,zhang2020adversarial,morris2020textattack,jin2020bert} and object detection \cite{wei2019transferable}.
Scenarios of possible adversarial attacks can be categorized along different dimensions.
